Title Goes Here

### 2017-09-14 analysis/paper/saa2018_general_sessions.Rmd
keywords per topic plot

```{r}
# run a loop over the abstract with different numbers of topics to find which number of topcis is the best
seqk <- seq(2, 100, 1)
burnin <- 1000
iter <- 1000
keep <- 50
```

@@

# plot it
library(ggplot2)
lda_plot <- ggplot(data.frame(seqk, 
                             hm_many_2018), 
                  aes(x=seqk, 
                      y=hm_many_2018)) + 
  geom_path(lwd=1.5)  +
  xlab('Number of Topics') +
  ylab('Harmonic Mean') +
  geom_vline(xintercept = seqk[which.max(hm_many_2018)],
             colour = "red") +
  annotate("text",
           x = 55, 
           y = -150000, 
           label = paste("The optimal number of topics is", 
                         seqk[which.max(hm_many_2018)])) +
  theme_bw() +
  ggtitle("Latent Dirichlet Allocation Analysis of SAA General Abstracts",
          subtitle = paste0("How many distinct topics are present in the general abstracts (n = ", how_many_abstracts, ") for 2018?"))
```

```{r}
# now run the model with the optimum number of topics
system.time(general_model <- topicmodels::LDA(general_reduced_dtm, 
                                              optimal_number_of_topics,
                                              method = "Gibbs", 
                                              control = list(iter=2000, 
                                                             seed = 0622)))

@@

```{r}
tidy_topics_top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
```

>>>>

```{r}
# run a loop over the abstract with different numbers of topics to find which number of topics is the best
seqk <- seq(2, 100, 1)
burnin <- 1000
iter <- 1000
keep <- 50
```

@@

# plot it
library(ggplot2)
lda_plot <- ggplot(data.frame(seqk, 
                             hm_many_2018), 
                  aes(x=seqk, 
                      y=hm_many_2018)) + 
  geom_path(lwd=1.5)  +
  xlab('Number of Topics') +
  ylab('Harmonic Mean') +
  geom_vline(xintercept = optimal_number_of_topics_2018,
             colour = "red") +
  annotate("text",
           x = 55, 
           y = -150000, 
           label = paste("The optimal number of topics is", 
                         optimal_number_of_topics_2018)) +
  theme_bw() +
  ggtitle("Latent Dirichlet Allocation Analysis of SAA General Abstracts",
          subtitle = paste0("How many distinct topics are present in the general abstracts (n = ", how_many_abstracts, ") for 2018?"))

ggsave("../figures/saa2018_general_abstracts_opti_topics.png")
```

```{r}
# now run the model with the optimum number of topics
system.time(general_model <- topicmodels::LDA(general_2018_reduced_dtm, 
                                              optimal_number_of_topics_2018,
                                              method = "Gibbs", 
                                              control = list(iter=2000, 
                                                             seed = 0622)))

@@

```{r}
# show top keywords for each topic
tidy_topics_top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()

ggsave("../figures/keywords_for_saa2018_general_topics.png", h = 14, w = 14)
```
